Supporting Information

### 2021-10-25 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
update
Changed records included in ROB plots
Cut off is 5296, plus preprints published afterwards

rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
#rob_records <- rob_records[rob_records$record_id < "5566", ]
rob_records <- rob_records[rob_records$record_id < 5296, ]

@@

dev.new()
png("q1_2_new.png", width = 1400, height = 2200)
p75
graphics.off()

>>>>

rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")

#censor until 5296 (31 Jan) plus the published versions of preprints
pub_preprints <- c(5565, 6219, 6685, 7030, 7465, 8249, 9442, 9484) #published version of preprints before 31 Jan
rob_records <- rob_records %>%
  filter(record_id %in%  pub_preprints | record_id <= 5296)

@@

dev.new()
png("q1_2_new.png", width = 1400, height = 2200)
p7
graphics.off()
